---
title: "Running a SARS-CoV-2 model with covidm"
author: "Nick Davies"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running a SARS-CoV-2 model with covidm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, load the `covidm` package.

```{r setup}
library(covidm)
```

# Heading 1

This will guide you to getting started with covidm.

## Heading 2

Really it will.

### Heading 3

OK, so it's not finished yet.

* Bulleted list
* Item 2
    * Nested bullets need a 4-space indent.
    * Item 2b


1.  Item 1.
    *  Item a
    *  Item b
1.  Item 2.

Definition
  : a statement of the exact meaning of a word, especially in a dictionary.

List 
  : a number of connected items or names written or printed consecutively, 
    typically one below the other. 
  : barriers enclosing an area for a jousting tournament.



_italic_ or *italic*

__bold__ or **bold**    

[link text](destination)

Note - to link to vignette abc.Rmd, link to abc.html

<http://this-is-a-raw-url.com>



| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |

```r
print("R code that is not run.")
```


```{r}
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
```
